### 2014-02-24 paper/retrofit.tex
typofix
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
Add lemma.

\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
  For any two list of tasks |its1|, |its2|, |its2|, label |il|,
  IFC states |iS1|, |iS2|, |iS1'|, where
  \begin{equation} \label{eq:tsni-lhs}
    |its1| \approx_{|il|} |its2|
    \qquad \text{and} \qquad
    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
  \end{equation}
  then there exists a list of tasks |ts2'| and an IFC state |iS2'| such that
  \begin{equation} \label{eq:tsni-rhs}
    |its1'| \approx_{|il|} |its2'|
     \qquad \text{and} \qquad
    |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
    \ \text{.}
  \end{equation}
\end{theorem}

>>>>

\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
  For any list of tasks |its1|, |its2|, |its2|, label |il|,
  IFC states |iS1|, |iS2|, |iS1'|, where
  \begin{equation} \label{eq:tsni-lhs}
    |its1| \approx_{|il|} |its2|
    \qquad \text{and} \qquad
    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
  \end{equation}
  then there exists a list of tasks |its2'| and an IFC state |iS2'| such that
  \begin{equation} \label{eq:tsni-rhs}
    |its1'| \approx_{|il|} |its2'|
     \qquad \text{and} \qquad
    |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
    \ \text{.}
  \end{equation}
\end{theorem}

\begin{lemma}
  For any list of tasks |its1|, |its2|, |its2|, label |il|,
  IFC states |iS1|, |iS2|, |iS1'|, where
  \begin{equation} \label{eq:tsni-lhs}
  |its1| \approx_{|il|} |its2|
  \qquad \text{and} \qquad
  |iconf iS1 its1| |.->| |iconf iS1' its1'|
  \end{equation}
  then there exists a list of tasks |its2'| and an IFC state |iS2'| such that
  \begin{equation} \label{eq:tsni-rhs}
  |its1'| \approx_{|il|} |its2'|
  \qquad \text{and} \qquad
  |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
  \ \text{.}
  \end{equation}
\end{lemma}
